
```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

```{r results="hide"}
library(tidyverse)
library(caret)
library(readxl)
library(stargazer)
library(e1071)
library(partykit)

set.seed(6527)
```

# Data

First, we read all non-standard uses which did not require preprocessing.

```{r}
he_ns <- read_excel("he_ns.xlsx")
she_ns <- read_excel("she_ns_1.xlsx")
she_ns <- rbind(she_ns, read_excel("she_ns_2.xlsx"))
they_ns <- read_excel("they_ns.xlsx")
```

Here, we label them as `ns` (non-standard).

```{r}
he_ns %>% 
  mutate(pron="he", type="ns") -> he_ns

she_ns %>% 
  mutate(pron="she", type="ns") -> she_ns


they_ns %>% 
  mutate(pron="they", type="ns") -> they_ns
```

Second, the preprocessed data on standard uses was loaded.

```{r}
he_s <- read_excel("standard_forms.xlsx", sheet = "he")
she_s <- read_excel("standard_forms.xlsx", sheet = "she")
they_s <- read_excel("standard_forms.xlsx", sheet = "they")
```

And labeled.

```{r}
he_s %>% 
  mutate(pron="he", type="s") -> he_s

she_s %>% 
  mutate(pron="she", type="s") -> she_s

they_s %>% 
  mutate(pron="they", type="s") -> they_s
```

Now, we combined them all together into one dataset.

```{r}
df <- rbind(he_ns, she_ns, they_ns, he_s, she_s, they_s)
```

The prepocessed file with metadata on speaker was loaded here. We also merge
our dataset with it and select only needed columns. 

```{r}
meta <- read_excel("metadata_unified.xlsx")
merge(df, meta, by.x = "person_id", by.y = "id") %>% 
  select(person_id, pron, type, gender, birthyear, birthplace,
         relative_to_mikh, education_school, education_add, job_norm,
         livingplace) -> final_data
```

Here, the data are preprocessed.

```{r}
final_data %>% 
  mutate(education_school = replace_na(as.numeric(education_school), 0),
         education_add = factor(education_add,
                                levels = c("-", "courses", "college", "university"))
         ) -> final_data

final_data[is.na(final_data)] <- "-"

final_data$pron <- as.factor(final_data$pron)
final_data$gender <- as.factor(final_data$gender)
final_data$relative_to_mikh <- as.factor(final_data$relative_to_mikh)
final_data$job_norm <- as.factor(final_data$job_norm)
final_data$livingplace <- as.factor(final_data$livingplace)
```

The summary is as follows.

```{r}
summary(final_data)
```

# Analysis

Now, we train Logistic Regression to understand what features are important in predicting type of a possessive pronoun. We used as predictors `gender`, `birthyear`,
`education` (both school and other than school), `birthplace relatively to Mikhalevskaja`. We did not include other features to minimize the number of parameters.

```{r}
final_data %>% 
  mutate(type = ifelse(type == "ns", 0, 1)) -> final_data

model <- glm(type ~ pron+gender+birthyear+education_school+education_add+relative_to_mikh,
            data=final_data)
stargazer(model,
          type="text",
          p.auto = TRUE,
          single.row=TRUE,
          ci=TRUE, ci.level=0.95,
          report='vscp*')
```

We check whether the model is adequate and is not disbalanced.

```{r}
pred <- predict(model)
pred <- ifelse(pred < 0.3, 0, 1)
confusionMatrix(data=as.factor(pred),
                reference = as.factor(final_data$type))
```

Now, we run a series of chi-square tests to check whether `type` is independent from other factors, namely `gender`, `birthyear`, `education_school`, `education_add`, and `relative_to_mikh`.

```{r}
final_data %>% 
  select(gender, type) %>% 
  table %>% 
  chisq.test(simulate.p.value=TRUE)

final_data %>% 
  select(birthyear, type) %>% 
  table %>% 
  chisq.test(simulate.p.value=TRUE)

final_data %>% 
  select(education_school, type) %>% 
  table %>% 
  chisq.test(simulate.p.value=TRUE)

final_data %>% 
  select(education_add, type) %>% 
  table %>% 
  chisq.test(simulate.p.value=TRUE)

final_data %>% 
  select(relative_to_mikh, type) %>% 
  table %>% 
  chisq.test(simulate.p.value=TRUE)
```

And the final model is a decision tree.

```{r}
final_data$birthplace <- NULL
final_data$person_id <- NULL

tree_type <- ctree(type ~ ., data=final_data)
plot(tree_type)
```

